---
title: "HW 2 DATA 613"
author: "remy sorensen"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

Problem 1:
Copy paste and run the tribble given below.
  library(tidyverse)
tribble( ~x,

  ~y,    ~w,    ~z,
210,   300,   220,   180,
102,   100,   119,   187,
176,   175,   188,   173,
87,    95,   91,     94,
202,   210,  234,    218,
110,   122,  131,    128,
) -> dt dt
```{r}
library(tidyverse)

tribble( ~x,
 ~y,    ~w,    ~z,
210,   300,   220,   180,
102,   100,   119,   187,
176,   175,   188,   173,
87,    95,   91,     94,
202,   210,  234,    218,
110,   122,  131,    128,
) -> dt 
dt
```

1_a:
• Use and show a map function to find the “mean” of each column of the dt data table 
1_b:
• Use and show a map function to find the “standard deviation” of each column of the dt data table.
1_c:
• Use and show a map function that will calculate the “square root” of each value of each column of the data table dt.