---
title: "hw2"
author: "remy sorensen"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggplot2)
library(purrr)
```

Problem 1:
Copy paste and run the tribble given below.
  library(tidyverse)
tribble( ~x,

  ~y,    ~w,    ~z,
210,   300,   220,   180,
102,   100,   119,   187,
176,   175,   188,   173,
87,    95,   91,     94,
202,   210,  234,    218,
110,   122,  131,    128,
) -> dt dt
```{r}
library(tidyverse)

tribble( ~x,
 ~y,    ~w,    ~z,
210,   300,   220,   180,
102,   100,   119,   187,
176,   175,   188,   173,
87,    95,   91,     94,
202,   210,  234,    218,
110,   122,  131,    128,
) -> dt 
dt
```

1_a:
• Use and show a map function to find the “mean” of each column of the dt data table 
```{r}
library(purrr)
map_dbl(dt, mean)
```

1_b:
• Use and show a map function to find the “standard deviation” of each column of the dt data table.
```{r}
library(purrr)
map(dt, sd)
```

1_c:
• Use and show a map function that will calculate the “square root” of each value of each column of the data table dt.
```{r}
map(dt, sqrt)
```

1_d:
• Use R code to find the “mean”, “max”, “1st Quartile”, “3rd Quartile”, “Median”, and “Min” for each column of the dt data table. (Hint: You do not have to use a map function)
```{r}
summary(dt)
```
Problem 2:
Write a function that uses a for loop that, for each iteration, randomly draws 5 observations from an exponential distribution with “rate” parameter 1 (use rexp()) and calculates its “mean”. It should do this 10,000 times. Choose an appropriate plot to plot the distribution of
“means”.
```{r}
draw_mean <- function() {
  mean(rexp(5, rate = 1))
}

```

2_a:
• Repeat part 1 by using a map_*() function. 
```{r}
means <- map_dbl(1:10000, ~draw_mean())

hist(means)
```

2_b:
• Repeat part 1 by using the replicate() function. 
```{r}
replicate_means <- replicate(10000, draw_mean())
hist(replicate_means)
```

2_c:
• Use a another for loop that will print out plots for sample sizes of 5, 10, and 20 observations (instead of just 5).
```{r}
new_draw_mean <- function(n) {
  mean(rexp(n, rate = 1))
}

samplen <- c(5, 10, 20)

for (n in samplen) {
  meansn <- replicate(10000, new_draw_mean(n))}

hist(meansn)
```

Problem 3:

• Use and show R coding to calculate the “standard deviation” for each variable of the data table mtcars using the “Special For Loop Method”.
```{r}
output <- vector("double", ncol(mtcars))  
for (i in seq_along(mtcars)) {
  output[[i]] <- median(mtcars[[i]])
} 
output
```

